---
#Hamadi, can you accept this test comment?
#Test 2
#Test 3
title: "REEFo_map"
author: "Hamadi Mwamlavya"
date: "15 April 2020"
output: html_document
---

```{r setup}
library(readxl) 
library(tidyverse)  
library(magrittr) 
library(ggpubr)
library(cowplot) 
library(sf) 
library(ggspatial)  
knitr::opts_chunk$set(echo = FALSE,message = FALSE,warning = FALSE, results = TRUE,include = TRUE, dpi=300, fig.width=1.5, fig.height=3)
```
## 1.Creating all the subplots to be included/appended on the main map
#Make a plot (pie chart) for the benthic data

```{r benthic}
benthic <- read_excel("benthic.xlsx")
benthic$Location <- as.factor(benthic$Location) #each number reps a sampling point

data <- gather(benthic, substrate, cover, Hard.coral:Other)

labels <- c("Hard.coral", "Soft.coral", "Turf.algae", "Macroalgae", "Other") #results in the pie chart to appear in this order

#Create a function to build piecharts to summarize data for 6 locations/sites

piechart <- function(x){
data.1 <- data %>% 
  filter(x) %>% 
  group_by(substrate) %>% 
  summarize(cover=mean(cover), samples=n()) %>%
  mutate(substrate = factor(substrate, levels = labels)) %>% 
  arrange(substrate)
  
ggplot(data = data.1, mapping = aes(x="", y=cover, fill=substrate)) +
  geom_bar(stat="identity", width=1) + 
  coord_polar("y",start = 0, direction = -1) +
  scale_fill_manual(values = c("#FF6600", "#FFFF66", "#66FF66", "#006600",
                               "#C4E7E8")) +
  theme_void(base_size = 2,base_family = 'serif') +
  theme(legend.position = "none")
}

#I need 6 objects to append to the two bar plots on fish biomass and urchin density

a.1 <- piechart(data$Location==1)
a.2 <- piechart(data$Location==2)
a.3 <- piechart(data$Location==3)
a.4 <- piechart(data$Location==4)
a.5 <- piechart(data$Location==5)
a.6 <- piechart(data$Location==6)
```

#Make a separate legend for the piechart on benthic cover
```{r}
data.2 <- data %>% 
  filter(Location==1) %>% 
  group_by(substrate) %>% 
  summarize(cover=mean(cover), samples=n()) %>%
  mutate(substrate = factor(substrate, levels = labels)) %>% 
  arrange(substrate)
guide.plot <- ggplot(data = data.2, mapping = aes(x="", y=cover, fill=substrate)) +
  geom_bar(stat="identity", width=1) +
  coord_polar("y",start = 0, direction = -1) + 
  scale_fill_manual(values = c("#FF6600", "#FFFF66", "#66FF66", "#006600",
                               "#C4E7E8"))+
  labs(fill="Substrate")+
  theme_void(base_size = 2,base_family = 'serif') + 
  theme(panel.grid = element_blank(),
        panel.border = element_rect(fill = NA, colour = "black"),
        legend.box.background = element_blank(),
        legend.text = element_text(size = 10.5),
        legend.position = c(.5,.5),
        legend.title = element_text(size=10.5,hjust = 0.5,
                                    vjust = 1, face = "bold"),
        panel.background = element_blank())
  
legend <- get_legend(guide.plot)
pie.legend <- as_ggplot(legend)
```


# Bar chart for urchin density

```{r urchins}
urchins <- read_excel("urchins.xlsx") 
urchins$Location <- as.factor(urchins$Location) 

#Create a function to plot summary of the 6 locations
urchin.chart <- function(x){
urchins.1 <- urchins %>% 
  filter(x) %>% #get summary for each location
  summarize(density=mean(density.m2), 
            sd = sd(density.m2),
            n=n(),
            se = sd/sqrt(n)) %>% 
  rownames_to_column("Location")

bbar <- ggplot(urchins.1, aes("", density))+
  geom_bar(stat="identity", width=1, fill="black") + 
  geom_errorbar(aes(ymin=density, ymax=density+sd), width=.1,
                 position=position_dodge(.9)) +
  scale_y_continuous(breaks = .5, limits = c(0, 2)) +
  labs(title = "", x = "", y = "") +
  theme(panel.grid = element_blank(),
        panel.background = element_blank(),
        axis.ticks.x = element_blank(),
        axis.line.y = element_line(colour = "black"),
        axis.line.x = element_blank())
  
#make the image strip
bimage <- axis_canvas(bbar, axis = 'x') + 
  draw_image("C:/Users/Hamadi.Mwamlavya/Dropbox/work.stuff/reefOLUTION/urchin.png",
             x = 0.5, scale = 4, vjust = 1.5)
  

#insert the image strip into the bar plot and draw  
ggdraw(insert_xaxis_grob(bbar, bimage, position = "bottom"))
}

b.1 <- urchin.chart(urchins$Location==1)
b.2 <- urchin.chart(urchins$Location==2)
b.3 <- urchin.chart(urchins$Location==3)
b.4 <- urchin.chart(urchins$Location==4)
b.5 <- urchin.chart(urchins$Location==5)
b.6 <- urchin.chart(urchins$Location==6)
```
#Make a descriptive plot for urchin density

```{r}
urchins.2 <- urchins %>% 
  filter(urchins$Location==2) %>% #get summary for each location
  summarize(density=mean(density.m2), 
            sd = sd(density.m2),
            n=n(),
            se = sd/sqrt(n)) %>% 
  rownames_to_column("Location")

urchin.guide <- ggplot(urchins.2, aes("", density))+
  geom_bar(stat="identity", width=1, fill="black")+ #plot a bar chart
  geom_errorbar(aes(ymin=density-sd, ymax=density+sd), width=.1,
                 position=position_dodge(.9))+
  scale_y_continuous(breaks = .5, limits = c(0, 2)) +
  labs(title = "Urchin/m2", x = "", y = "") +
  theme(panel.grid = element_blank(),
        panel.background = element_blank(),
        axis.ticks.x = element_blank(),
        axis.line.y = element_line(colour = "black"),
        axis.line.x = element_blank(),
        plot.title = element_text(size=10, face="bold"))
  
# make the image strip
uimage <- axis_canvas(urchin.guide, axis = 'x') + 
  draw_image("C:/Users/Hamadi.Mwamlavya/Dropbox/work.stuff/reefOLUTION/urchin.png",
             x = 0.5, scale = 4, vjust = 1.5)
  
# insert the image strip into the bar plot and draw  
urchin.plot <- ggdraw(insert_xaxis_grob(urchin.guide, uimage, position = "bottom"))
```

# Bar chart for fish biomass

```{r fish}
fishes <- read_excel("fishes.xlsx") 
fishes$Location <- as.factor(fishes$Location) 

fish.chart <- function(x){
fishes.1 <- fishes %>% 
  filter(x) %>%
  summarize(biomass = mean(biomass.kg.ha), 
            sd = sd(biomass.kg.ha),
            n = n(),
            se = sd/sqrt(n)) %>% 
  rownames_to_column("Location")

cbar <- ggplot(fishes.1, aes("", biomass))+
  geom_bar(stat = "identity", width = 1, fill = "black")+ #plot a bar chart
  geom_errorbar(aes(ymin = biomass, ymax = biomass+sd), width = .1,
                position = position_dodge(.9))+
  scale_y_continuous(breaks = 150, limits = c(0,2000))+
  labs(title = "", x = "", y = "")+
  theme(panel.grid = element_blank(),
        panel.background = element_blank(),
        axis.ticks.x = element_blank(),
        axis.line.y = element_line(colour = "black"),
        axis.line.x = element_blank())
  
# make the image strip
cimage <- axis_canvas(cbar, axis = 'x') + 
  draw_image("C:/Users/Hamadi.Mwamlavya/Dropbox/work.stuff/reefOLUTION/fish.png", 
             x = 0.4, scale = 1.9, vjust = 1.5)
  

# insert the image strip into the bar plot and draw  
ggdraw(insert_xaxis_grob(cbar, cimage, position = "bottom"))
}

c.1 <- fish.chart(fishes$Location==1)
c.2 <- fish.chart(fishes$Location==2)
c.3 <- fish.chart(fishes$Location==3)
c.4 <- fish.chart(fishes$Location==4)
c.5 <- fish.chart(fishes$Location==5)
c.6 <- fish.chart(fishes$Location==6)
```
#Make a descriptive plot for fish biomass
```{r}
fishes.2 <- fishes %>% 
  filter(fishes$Location==1) %>% 
  summarize(biomass = mean(biomass.kg.ha), 
            sd = sd(biomass.kg.ha),
            n = n(),
            se = sd/sqrt(n)) %>% 
  rownames_to_column("Location")

# make the barplot
fish.guide <- ggplot(fishes.2, aes("", biomass))+
  geom_bar(stat = "identity", width = 1, fill = "black")+ #plot a bar chart
  geom_errorbar(aes(ymin = biomass-sd, ymax = biomass+sd), width = .1,
                position = position_dodge(.9))+
  scale_y_continuous(breaks = 150, limits = c(0,500))+
  labs(title = "Fish kg/ha", x = "", y = "")+
  theme(panel.grid = element_blank(),
        panel.background = element_blank(),
        axis.ticks.x = element_blank(),
        axis.line.y = element_line(colour = "black"),
        axis.line.x = element_blank(),
        plot.title = element_text(size=10, face="bold"))

# make the image strip
fimage <- axis_canvas(fish.guide, axis = 'x') +
  draw_image("C:/Users/Hamadi.Mwamlavya/Dropbox/work.stuff/reefOLUTION/fish.png", 
             x = 0.4, scale = 1.9, vjust = 1.5)
  
# insert the image strip into the bar plot and draw  
fish.plot <- ggdraw(insert_xaxis_grob(fish.guide, fimage, position = "bottom"))
```
# Combine the 3 plots; benthic cover pie chart, fish biomass plot and urchin density plot

```{r locations}
loc.0 <- ggarrange(pie.legend,fish.plot,urchin.plot,widths = c(7,7.1,7),nrow = 1)+
  theme(panel.border = element_rect(fill = NA, colour = "black"))

d.1 <- ggarrange(a.1,c.1,b.1,widths = c(7,7.1,7), nrow = 1)
loc.1 <- annotate_figure(d.1,fig.lab = "1", fig.lab.face = "bold", 
                         fig.lab.size = 20)+
  theme(panel.border = element_rect(fill = NA, colour = "black"))

d.2 <- ggarrange(a.2,c.2,b.2,widths = c(7,7.1,7), nrow = 1)
loc.2 <- annotate_figure(d.2,fig.lab = "2", fig.lab.face = "bold", 
                         fig.lab.size = 20)+
  theme(panel.border = element_rect(fill = NA, colour = "black"))


d.3 <- ggarrange(a.3,c.3,b.3,widths = c(7,7.1,7), nrow = 1)
loc.3 <- annotate_figure(d.3,fig.lab = "3", fig.lab.face = "bold", 
                         fig.lab.size = 20)+
  theme(panel.border = element_rect(fill = NA, colour = "black"))

d.4 <- ggarrange(a.4,c.4,b.4,widths = c(7,7.1,7), nrow = 1)
loc.4 <- annotate_figure(d.4,fig.lab = "4", 
                         fig.lab.face = "bold", fig.lab.size = 20)+
  theme(panel.border = element_rect(fill = NA, colour = "black"))


d.5 <- ggarrange(a.5,c.5,b.5,widths = c(7,7.1,7), nrow = 1)
loc.5 <- annotate_figure(d.5,fig.lab = "5", fig.lab.face = "bold", 
                         fig.lab.size = 20)+
  theme(panel.border = element_rect(fill = NA, colour = "black"))

d.6 <- ggarrange(a.6,c.6,b.6,widths = c(7,7.1,7), nrow = 1)
loc.6 <- annotate_figure(d.6,fig.lab = "6", fig.lab.face = "bold", 
                         fig.lab.size = 20)+
  theme(panel.border = element_rect(fill = NA, colour = "black"))
```

## Create the main map - map of shimoni

```{r}
#spatial information for the 6 locations/study points
locations <- read_excel("locations.xlsx")
locations <- st_as_sf(locations, coords = c("Long", "Lat"), crs = 4326, 
    agr = "constant")

shim.town <- data.frame(
  site=c('Shimoni','Wasini','Kisite/Mpunguti Marine Protected Area'),
  lat=c(-4.639,-4.663,-4.703),
  long=c(39.382,39.377,39.366))

#shapefiles to build main map

reef <- st_read(dsn = "C:/Users/Hamadi.Mwamlavya/Dropbox/work.stuff/GIS/Kenya/Coral_reefs",layer = "ke_coral_reefs")

kisite <- st_read(dsn = "C:/Users/Hamadi.Mwamlavya/Dropbox/work.stuff/GIS/Kenya/Kisite-Mpunguti_MPA",layer = "Kisite-Mpunguti_MPA")
kisite <- st_transform(kisite,"+proj=longlat +datum=WGS84")

ke.county <- st_read(dsn = "C:/Users/Hamadi.Mwamlavya/Dropbox/work.stuff/GIS/Kenya/District_boundaries",layer = "ke_district_boundaries")

ke.country <- st_read(dsn = "C:/Users/Hamadi.Mwamlavya/Dropbox/work.stuff/GIS/Kenya/KEN_outline_SHP",layer = "KEN_outline")
ke.country <- st_set_crs(ke.country,"+proj=longlat +datum=WGS84")

wasini_cca <- st_read(dsn = "C:/Users/Hamadi.Mwamlavya/Dropbox/work.stuff/GIS/Kenya/Wasini_CCA", layer = "Wasini_cca")

#inset
kenya <- ggplot() + 
  geom_sf(data=ke.country, color = 'black', fill = 'white') +
  annotate("rect", xmin = 39, xmax = 39.7, ymin = -4, ymax = -5,alpha = .5,color='blue',fill=NA,size=.8) +
  annotate("text",x=38,y=0,label="Kenya", size=4) +
  coord_sf() + labs(x = NULL, y = NULL) +
  theme_void()+
  theme(panel.border = element_rect(fill = NA, colour = "black"),
        plot.background = element_rect(fill = "grey") )
  
#main map 
shimoni <- ggplot() +
  geom_sf(data = ke.county, color = 'black', fill = 'antiquewhite1')+
  geom_sf(data = kisite,aes(fill = GISNAME),alpha = .25)+
  geom_sf(data = reef, aes(color = ''))+
  geom_sf(data = wasini_cca,fill="brown1",alpha = .25)+
  geom_sf(data = locations, shape=21,color="black",
          size=4.5, fill = locations$Colors)+
  annotate("text",x=shim.town$long,y=shim.town$lat,
           label=shim.town$site,vjust=.1,size=6)+
  coord_sf(xlim = c(39.309,39.440),ylim = c(-4.79,-4.630))+
  labs(x=NULL,y=NULL) + 
  scale_y_continuous(breaks = c(-4.64,-4.69,-4.74))+
  scale_x_continuous(breaks = c(39.34,39.38,39.42))+
  scale_fill_manual(values = c("brown1","SpringGreen3","blue"),
                    name="Legend",
                    labels= c("Marine park","Marine reserve","Study site"))+
  scale_color_manual(values = c("darkturquoise"),
                    name="",
                    labels= c("Coral reef"))+
  theme(panel.grid = element_blank(),
        panel.border = element_rect(fill = NA, colour = "black",size = 2.5),
        legend.box.background = element_blank(),
        legend.text = element_text(size = 16),
        legend.title = element_text(size=16,hjust = 0.5,vjust = 1),
        legend.position = c(.6,.15),
        legend.box = "horizontal",
        panel.background = element_blank())
        
shimoni.site <- shimoni + 
  annotation_scale(location = "br", width_hint = 0.5) +
  annotation_north_arrow(location = "tr", which_north = "true",
                         pad_x = unit(.2, "in"), 
                         pad_y = unit(.2, "in"),
                         style = north_arrow_fancy_orienteering)
shimoni.site <- ggdraw(shimoni.site) +
  draw_plot(kenya, width = 0.15, height = 0.15 * 10/6 * .8625, 
        x = 0.085, y = 0.79)

#location of arrows in the plot
arrowA <- data.frame(x1 = 23.8, x2 = 32.3 , y1 = 19.7, y2 = 19.7)
arrowB <- data.frame(x1 = 23, x2 = 32.3, y1 = 18.7, y2 = 17.4)
arrowC <- data.frame(x1 = 24.98, x2 = 32.3, y1 = 15.2, y2 = 12.4)
arrowD <- data.frame(x1 = 26.6, x2 = 32.3, y1 = 13.4, y2 = 7)
arrowE <- data.frame(x1 = 22.1, x2 = 11.2, y1 = 12.3, y2 = 7)
arrowF <- data.frame(x1 = 20.3, x2 = 11.2, y1 = 19.1, y2 = 13.4)

#bringing everything together; combined plots + arrows + map
map <- ggdraw(xlim = c(0, 44), ylim = c(0, 26)) +
  draw_plot(shimoni.site, x = 11.2, y = 3, width = 20, height = 20) +
  draw_plot(loc.1, x = 32.5, y = 18.5, width = 9*1.2, height = 4) +
  draw_plot(loc.2, x = 32.5, y = 13.8, width = 9*1.2, height = 4) +
  draw_plot(loc.3, x = 32.5, y = 8.8, width = 9*1.2, height = 4) +
  draw_plot(loc.4, x = 32.5, y = 4, width = 9*1.2, height = 4) +
  draw_plot(loc.0, x = .25, y = 18.3, width = 9*1.2, height = 4) +
  draw_plot(loc.6, x = .25, y = 10, width = 9*1.2, height = 4) +
  draw_plot(loc.5, x = .25, y = 4., width = 9*1.2, height = 4) +
  geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2), data = arrowA,
               lineend = "round") +
  geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2), data = arrowB,
               lineend = "round") +
  geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2), data = arrowC,
               lineend = "round") +
  geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2), data = arrowD,
               lineend = "round") +
  geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2), data = arrowE,
               lineend = "round") +
  geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2), data = arrowF,
               lineend = "round")

ggsave("opacity_,25.png", width = 10*1.42, height = 10, dpi = 900)
```

